---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Motivation

> If you’re asking for R help, reporting a bug, or requesting a new feature,
> you’re more likely to succeed if you include a good reprex.
--https://reprex.tidyverse.org/articles/reprex-dos-and-donts.html

## Overview

### Setup

You can use reprex with `library()`.

```{r}
library(reprex)
```

But it's safe to add to .Rprofile so it's always available.

```
if (interactive()) {
  suppressMessages(require(reprex))
}
```

### Example

This example shows a bug that was fixed a while ago
(https://github.com/r-lib/fs/issues/205).

This is unexpected:

```{r}
library(fs)
packageVersion("fs")

files <- c("a", "b")
path_ext_set(files, ".csv")
```

#### Create a reprex

You can create a reprex in multiple ways.

* Select > Addins > "Reprex selection"
* Copy > `reprex()`
* Copy > `reprex(session_info = TRUE)`
* Copy > `reprex(venue = "r")`
* `reprex(input = "01_overview/issue-205_reprex.R")`
* `reprex({ (multi-line) expression })`
* Select > Addins > "Render reprex"

#### Run a reprex

Reprex shows output, so the reader doesn't *have to* run the code.

If they want, they can copy-paste and run it, because the output is commented.

#### Clean a reprex

They can reuse your reprex easily with copy + `reprex_clean()`

#### A not-so reprex on your working directory

Sometimes you have no choice and must run reprex in your working directory:

```r
reprex(wd = ".", {

  library(fs)
  packageVersion("fs")
  
  paths <- readRDS("01_overview/paths.rds")
  path_ext_set(paths, ".csv")
  
})
```

